Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{ Funded by DARPA Cyber Assured Systems Engineering (CASE) contract HR00111890001. }

### 2021-05-06 paper/example.tex
Update system model

\newsavebox{\flt}
\begin{lrbox}{\flt}
\begin{lstlisting}[style=agree]
property CASE_Filter_policy = 
  WELL_FORMED_AUTOMATION_RESPONSE(Input);
guarantee CASE_Filter_Output "Filter output is well-formed" :
  if event(Input) and CASE_Filter_policy then
    event(Output) and Output = Input
  else not event(Output);
\end{lstlisting}
\end{lrbox}

\newsavebox{\mntr}
\begin{lrbox}{\mntr}
\begin{lstlisting}[style=agree]
const is_latched : bool = 
  Get_Property(this, CASE_Properties::Monitor_Latched);
eq rsp : bool = event(Response);
eq req : bool = event(Request);
eq nothing : bool = (not req) -> (not pre (req)) and (not req);
eq today : bool = req and rsp;    
eq yesterday : bool = false -> pre (req and not rsp);
property policy = nothing
                or (today and not yesterday)
                or (not today and rsp and yesterday);
eq alert : bool = (not policy) 
               -> ((is_latched and pre(alert)) or not policy);

guarantee "Alert port tracks alert variable" :
    event(Alert) <=> alert;
guarantee "Output if not alerted" :
    if event(Alert) then (not event(Output)) else
    if event(Response) then (event(Output) and (Output = Response))
    else (not event(Output));
\end{lstlisting}
\end{lrbox}

@@

The system implementation is cyber-hardened by inserting high-assurance components in the form of a filter and a monitor as shown in \figref{fig:hardened}(a). A filter enforces an invariant over each datum in the data stream by not forwarding input to its output if that input is violating. Its stylized form generated the CASE tools is shown in \figref{fig:assurance}(a). The user must provide the meaning of the property, which is just a predicate, while the tool generates everything else. In this example, the property is the assumption made by the waypoint manager about the automation response being well-formed. The guarantee is such that it has a trivial direct mapping to synthesized code by completely specifying the behavior of the output.

A monitor captures a relation over time on data and is able to reason about temporal properties. In this example, the monitor only forwards responses that meet the bounded response property as shown in \figref{fig:assurance}(b). Like the filter, the generated monitor, with its contract, is stylized for synthesis only requiring the user to indicate the policy and some extra information for the outputs. The policy is taken from the contract in \figref{fig:sw} since it is the monitor that needs to alert violations of the bounded response policy.

>>>>

\newsavebox{\flt}
\begin{lrbox}{\flt}
\begin{lstlisting}[style=agree]
eq policy : bool = WELL_FORMED_AUTOMATION_RESPONSE(Input);
property Policy_Output = 
      if event(Input) and policy then 
        event(Output) and Output = Input
      else not event(Output);
guarantee "Filter output is well-formed" :
    Policy_Output;
\end{lstlisting}
\end{lrbox}

\newsavebox{\mntr}
\begin{lrbox}{\mntr}
\begin{lstlisting}[style=agree]
const is_latched : bool = 
  Get_Property(this, CASE_Properties::Monitor_Latched);
eq rsp : bool = event(Response);
eq req : bool = event(Request);
eq nothing : bool = (not req) -> (not pre (req)) and (not req);
eq today : bool = req and rsp;    
eq yesterday : bool = false -> pre (req and not rsp);
eq policy: bool = nothing
                or (today and not yesterday)
                or (not today and rsp and yesterday);
eq alert : bool = (not policy) 
                -> ((is_latched and pre(alert)) or not policy);
property Policy_Output = 
  if event(Alert) then (not event(Output)) else
  if event(Response) then (event(Output) and (Output = Response))
  else (not event(Output));
property Policy_Alert =  event(Alert) = alert;

guarantee "Alert port tracks alert variable" :
    Policy_Alert;
guarantee "Output if not alerted" :
    Policy_Output;
\end{lstlisting}
\end{lrbox}

@@

The system implementation is cyber-hardened by using the CASE tools to insert high-assurance components in the form of a filter and a monitor as shown in \figref{fig:hardened}(a). A filter enforces an invariant over each datum in the data stream by not forwarding input to its output if that input is violating. Its stylized form as generated by the tool is shown in \figref{fig:assurance}(a). The user must declare the meaning of the \texttt{policy} value as part of the transform on the model. In this example, \texttt{policy} is the assumption made by the waypoint manager about the automation response being well-formed. The output policies and guarantees are automatically generated by the tool.

A monitor captures a relation over time on input data and is able to reason about temporal properties of that input. By definition, it raises an alert output when the relation is violated. The generated monitor contract is shown in \figref{fig:assurance}(b). The \texttt{is\_latched} value makes the alert persistent meaning that once raised always raised. The definition for \texttt{policy} is taken from the contract in \figref{fig:sw} since this high-assurance component is the monitor that needs to alert violations of the bounded response policy. As before the policies for the outputs and the guarantees are autogenerated by the tool.

### 2021-05-06 paper/system.tex
Update system model

\begin{figure}
  \[
    \begin{array}{rcl}
      \mathit{c}    & = & \konst{input}\ [(f : \tau)\ldots] \\
                    &   & \konst{output}\ [(f : \tau)\ldots] \\
                    &   & [\mathit{stmts}\ldots] \\
                    &   & \konst{assume}\ [\mathit{bexp}\ldots] \\
                    &   & \konst{guarantee}\ [\mathit{bexp}\ldots] \\ \\

      \mathit{stmts}& = & \konst{subcomp}\ \lval\dots\ c \\
                    & | & \konst{eq}\; f : \tau := \mathit{exp} \\ \\

@@

      \mathit{bexp} & = & \konst{bLoc}\; \lval
                          \mid  \konst{bLit}\; \konst{bool}
                          \mid  \neg \mathit{bexp}
                          \mid  \mathit{bexp} \land \mathit{bexp} \\
                    & | & \mathit{exp} = \mathit{exp} 
                    \mid  \mathit{exp} < \mathit{exp}
\end{array}
\]
\caption{Syntax for component specifications.}
\label{fig:syntax}
\end{figure}

A \emph{system} in this model of computation is a \emph{component} that is defined by a specification (see \figref{fig:syntax}). A specification defines inputs, outputs, statements, assumptions for pre-conditions, and guarantees for post-conditions. A statement can be a subcomponent definition with its input binding or a local variable definition.

A type $\tau$ is a contiguity type which is a self-describing dependent type specification (add citation). An $\lval$ is a reference to an \emph{L-value} from compiler concepts and is an expression that can appear on the left hand side of an assignment. Alpha renaming is assumed so that every $\lval$ is unique.

@@

The initial environment stream only contains mappings for primary inputs along the entire stream. Stepping the component updates the current environment. In other words, at the $i^\mathrm{th}$ step, $\theta^i$ is updated with the result of each component evaluation. A component step traverses the component sequentially to update the environment recursing into subcomponents after binding inputs. Assume the component is written in dependency order.

>>>>

\begin{figure}
  \[
    \begin{array}{rcl}
      \mathit{c}    & = & \konst{input}\ [(f : \tau)\ldots] \\
                    &   & \konst{output}\ [(f : \tau)\ldots] \\
                    &   & \konst{eq}\; f : \tau := \mathit{exp} \\
                    &   & \konst{policies}\ [\mathit{bexp}\ldots]\\

@@

      \mathit{bexp} & = & \konst{bLoc}\; \lval
                          \mid  \konst{bLit}\; \konst{bool}
                          \mid  \neg \mathit{bexp}
                          \mid  \mathit{bexp} \land \mathit{bexp} \\
                    & | & \mathit{exp} = \mathit{exp} 
                    \mid  \mathit{exp} < \mathit{exp}
\end{array}
\]
\caption{Syntax for high-assurance component specifications.}
\label{fig:syntax}
\end{figure}

The specification language for high-assurance components is in (see \figref{fig:syntax}). It is stylized contracts that defines the inputs, outputs, local values, and policies for each output. Each output policy must be invariant over the input stream and completely define the meaning of its corresponding output. A type $\tau$ is a contiguity type which is a self-describing dependent type specification (add citation). An $\lval$ is a reference to an \emph{L-value} from compiler concepts and is an expression that can appear on the left hand side of an assignment. Alpha renaming is assumed so that every $\lval$ is unique.

@@

The initial environment stream only contains mappings for the inputs along the entire stream. Stepping the component updates the current environment and checks the policies. In other words, at the $i^\mathrm{th}$ step, $\theta^i$ is updated with the result of the sequential evaluation of the \konst{eq}-statements in the specification, which are assumed to be in dependency order, and then the policies are checked for invariance.
